---
title: "FacebookBirthdays"
output: html_document
---



```{r}
library(ggplot2)

setwd('C:/Users/Sarah/Documents/R Files/EDA/GapMinder Lesson 3/EDA Project files')
list.files()

FriendsBirthdays <- read.csv('Birthdays.csv')
dates <- FriendsBirthdays$Start.Date
dates <- strptime(dates, format="%m/%d/%Y")
birthdays = data.frame(date=dates, month=strftime(dates, "%m"), day=strftime(dates, "%d"))
birthdays$month <- factor(birthdays$month, labels = c("January","February","March", "April","May","June","July","August","September", "October","November","December"), ordered=TRUE)

str(birthdays)
View(birthdays)
rm(FriendsBirthdays)
rm(dates)



```
There are 583 birthdays in the dataset.

# How many people share your birthday? Do you know them?
# (Reserve time with them or save money to buy them a gift!) 
3
```{r}
length(subset(birthdays, month == 9 & day == 30))
```


# Which month contains the most number of birthdays?
October
```{r}
qplot(x=month, data=birthdays, fill=month, 
      xlab = "Month",
      ylab = "Number of birthdays")
ggsave("birthdayByMonth.jpg")

```
# How many birthdays are in each month?
 January  February     March     April       May      June 
       45        38        38        39        62        51 
     July    August September   October  November  December 
       43        45        44        67        56        55 
```{r}
table(birthdays$month)
```
# Which day of the year has the most number of birthdays?
May 11
```{r}
which.max(table(birthdays$date))
```
# Do you have at least 365 friends that have birthdays on everyday of the year?
No. There are some days with no birthdays
```{r}
library(dplyr)
birthdays$md <- paste(birthdays$month, birthdays$day, sep=" - ")
qplot(x=md, data = birthdays,
      xlab = "Month- Day",
      ylab = "Number of birthdays")
```